---
title: "Procedure"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
```



```{r}
# Search Settings
# Global filters for all queries to the concept table
vocabulary_id <- c("SNOMED")
concept_class_id <- NULL
domain_id <- "Observation"
standard_concepts <- NULL
invalid_reasons <- c(NA, "NA")

# Project Setup
project_name <- "CBIOPORTAL"
origin_fn <-  "~/Memorial Sloan Kettering Cancer Center/cBioPortal Standardization - KMI Only - KMI Only/Mapping Files/cBioPortal_Workfile.xlsx"
origin_tab <- "MAP_20"


# Target Columns: column where queries are sourced from. Note that the column called "CONCEPT" has been changed to "SOURCE" in this routine since the merge of OMOP concepts is functionalized to be called `Concept`.
## Source Columns: 1:1 concepts
#input_file_stem <- "ESOPHAGUS_"
source_col <- "ONCOTREE_NAME"
word_split <- "[ ]{1}|[(]{1}|[)]{1}|[,]{1}|[/]{1}|[+]{1}|[-]{1}[>]{1}" #The regex to split() the SOURCE column on to retrieve words for words-based searches

## Term Columns: series of search terms and phrases to each original concept to further search for the concept. Term columns are manually inputed by an end-user.
term_col <- NULL

# Terminal Column: name of the column in the input that, if populated, indicates that a concept has been mapped and further search routines are ignored
terminal_col <- "Fact"
attribute_col <- NULL

regimen_col <- NULL
component_col <- NULL

# Skip parameters: parameters that signals skipping over a concept
source_skip_nchar <- 3
additional_filters <- NULL

#Additional filters fed into the dplyr filter function to apply to the input. Comment out if no filters should be applied.

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

